---
title: "User Guide of Cargo Data Miner"
author: "Xuzhou Qin"
date: "10 August 2016"
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: tex/header.tex
    number_sections: yes
    toc: yes
    toc_depth: 3
  word_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newpage

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

\subsection*{Abstract}
This is the user guide of *Cargo Data Miner*. *Cargo Data Miner* is an R-Shiny Dashboard application developed by Airbus Freighter Marketing department (CSMX). The initiative is to build a platform where everybody could query and analyze cargo data. In this document, detailed information and instruction are provided in order to facilitate the usage and maintenance of the application. For more information, the author could be reached at <xuzhou.qin@gmail.com>.

\subsection*{Acknowledgement}
The present work benefited from Oliver Von-Tronchin, tutor of my internship and director of Freighter Marketing (CSMX), Sebastian Aponte, Nicolas Chauviere-Courcol, colleagues of mine in CSMX, Federico Semeraro and Andy Williams, for their inspiration of the project *LiMA*, Pierre Binet, Didier Gauzy, Aurelien Turina, Sam Crawshay Jones, Lionel Cousseins, Yves Renard and all my colleagues of Airbus who provided valuable comments and ideas to the undertaking of the project here.



\newpage
# Introduction
Aviation market is a highly complex and data-dependent market. Inside Airbus, numbers of different servers are deployed to stock, manage and provide database services to support our daily work. It is striving to introduce data digitalization as a core task of its future plan. The raising importance of data has already grabbed the attention of the managers and it will never stop growing. However, face to the massive amount of data, challenge still remains. 

At the company level, the main challenge comes from the database management. Too many databases are stocked seperately with different **database management system** (DBMS). The databases are quite isolated from the others. In other words, except people who frequently use one database, others could not even know its existence. Then, the different DBMS cause inconvinience in database management. For example in the freighter marketing department (CSMX), three marketing databases, *Cargo IS*, *Seabury* and *FlightRadar 24* are stocked separately in three data servers using three different DBMS (Oracle Database, MySQL and Microsoft SQL server). 

At the department level, the major challenge is the lack of an efficient and user-friendly tool for the data extraction and analysis process. Even thought the traditional approach of database management, SQL, is widely used for data manipulation. But in order to use it efficiently, you must have some knowledge of programming and you have to suffer the difficulty in interfacing. As SQL is not a common tool inside marketing department, interacting with the data by using SQL may not be a suitable choice. As to the data analysis tool, Excel is one of the most widly used software. But it suffers from some innate limitations facing the increasing amount of data.

There are also some Airbus-made tools for marketing department, like *Acper*, *OAG Builder*, *route06*, etc. These are very powerful and sophisticated programs dedicated for specific usage since a very long time. They are irreplaceable for some tasks but they are still not perfect. For example, in terms of learning difficulty, they both have a steep learning curve. Some special training session are needed to master these tools. And from a graphical design's point of view, they often remind me about the "old fashioned" software interface, which may be not enough intuitive and user-friendly. The need to visualize the analytic results in a modern way is thus urgent.

Due to these facts, data digitalization inside Airbus could be done from two level. We will need an uniform and standardized platform to stock and manage data at the company level. And inside the departments, new data mining and analysis tools are needed to support the works in the big data era. Some moves have already been realized inside Airbus. **BIO** is a platform which provide an automatic aggregation of different databases. **Foundry** is a cloud-based platform for collaboratively big data analysis built by Palantir Technologies.

This document provide a feasible solution for the development of a data analysis tool by using **R Shiny Dashboard**. **Shiny Dashboard** is a framework to create a light weight, powerful and interactive web application. It uses a reactive programming model so that outputs change instantly as users modify inputs. It is easy to use, no web designing language required. But further customization could be easily done with some HTML, CSS and JavaScript knowledge. 

In the first section of this document, I will explain the reason for which **CDM** was born. After that, the installation and deployment prerequisites are presented. Then, detailed functionalities and the application structure, as well as the data structure, are stated in section two in order to provide technical support for using and maintenance. In the third section, some suggestions for the future development of this application are proposed. The technical appendix could be found in the last section of the document.


<!-- # Prerequisites -->

# Why R shiny Dashboard?

At the beginning of my internship, I have been asked to explore different cargo databases. Because of my statistical profile, I was using R to analyze and visualize these data. Lots of codes were written at that moment, as well as numbers of power-point slides. But my tutor and I realized that coding in R could not be a permanent solution for the needs of Freight Marketing (CSMX) team. Because the R is not a common tool inside marketing department and it is not that easy to learn for people with little programming knowledge.

I started looking for a good way to make a reusable, easy-to-access but powerful data analytic tool. I learnt a lot about R at school so my first intention is to keep using R as the programming language. Furthermore, the numbers of R users at Airbus is increating steadly. It could be a big advantage for the further development of the code. 

Shiny by Rstudio is a great tool that will fit our needs. Shiny offers the *reactive programming* framework that will fit perfectly our needs of a reusable tool. It allow us to produce different analysis from different inputs, without modifying the code. Meanwhile, the abundant R packages could make the life much better by dramatically reducing the programming work.

What else? By using Shiny Dashboard, it is easy to integrate different shiny applications into a one-page web application. So that we will have one complex dashboard based on [**Bootstrap 3**](https://github.com/twbs/bootstrap) framework. It is intuitive, efficient and polyvalent.

It has been four months since I started to develop **CDM**. Now the basic framework is almost done. In ther future, I wish that it could be helpful to make our work more efficient.


# Deployment guide

**Cargo Data Miner** (CDM) was developed with [**Microsoft R Open 3.2.5**](https://mran.revolutionanalytics.com/), which is a enhanced distribution of R. It support by default multi-thread computing and it is perfectly compatible with the [original **R**](https://www.r-project.org/). The user interface used during the development is [**RStudio**](https://www.rstudio.com/), which the the most common IDE of R.

To make **CMD** work properly, there are two main methods.

> -- Install and run it locally on a PC for personal use.

> -- Deploy it on a Shiny server so that CDM could be reached by an IP adress.

In this section, I will present both the two methods.


## Directory Structure

The following figure presents the structure of the CDM directory.

\begin{figure}[!h]
  \centering
  \includegraphics[width=300px]{img/structure.png}
  \caption{CDM directory structure}
\end{figure}

The main directory `~/CDM` contains Shiny Dashboard scripts (*ui.R*, *server.R* and *global.R*) and three directories: 

 * `/www` 

 * `/Rscripts` 
 
 * `/Rpackages` 

 * `/CDM_user_manuel`

All the images, HTML, CSS and JavaScript used in **CDM** should be placed in `~/CDM/www`. All the R scripts called by the application should be placed in `~/CDM/Rscripts` and all the R packages (for local installation) should be placed in `~/CDM/Rpackages`.These three directories are the essential parts of **CDM**.

In `~/CDM/CDM_user_manuel`, you will find the code of this use guide (written in R markdown) and its resources. All figures appeared in this document should be placed in `~/CDM/CDM_user_manuel/img` and all the LaTex scripts called from the R markdown code will be found in `~/CDM/CDM_user_manuel/tex`.


## Installation on a PC

**CDM** could run on a personal computer having installed R and a web browser with the correct configuration. Before the first use, some steps have to be followed.

* Step 1: Get R and other required software:
    + Install [**Microsoft R Open 3.2.5** from https://mran.revolutionanalytics.com/download/](https://mran.revolutionanalytics.com/download/) (to turn on the multi-thread computing support, install the MLK package as well), or you can install the [original **R** (64-bit) from https://cran.r-project.org/mirrors.html](https://cran.r-project.org/mirrors.html).
    
    + Install [**RStuido** from https://www.rstudio.com/products/rstudio/](https://www.rstudio.com/products/rstudio/). This is optional but \underline{highly recommended}. 
    
    + **CDM** works with Internet Explorer but you could also install [Google Chrome](https://www.google.fr/chrome/browser/desktop/) for the best performance.
    
    + Install **Oracle Database Instant Client (11.2.0.3) EN_W764** from PC service. Or you can download it from Oracle website (Make sure it is the 64-bit version). If error of Oracle occurs during the execution of **CMD**, see Appendix: Troubleshooting for help.
    
* Step 2: Connection Setup

    + **CMD** will need the access right of three different databases. They are: **p595dodmp01** (Cargo IS, Seabury), **fr0-bio-p01** (BIO) and **fr0-dmds-p01** (FlightRadar 24). The user name and password are already pre-filled and there is no need to change, except for **BIO** database. Because you will need to grant the access right to your own *Windows* account to make the connection. To do so, you could ask *Aurelien Turina* (<aurelien.turina@airbus.com>) or *Pierre Binet* (<pierre.binet@airbus.com>) for further information.

    + `~/CDM/server.R` contains the connection parameters of these databases.  

```{r eval = FALSE, echo = TRUE}
##########################################################
#' CONNECTION PARAMETERS
#' 
#' Modify it before the first execution of the application
##########################################################
#' ROracle connection string
#' for Cargo IS, Seabury
host = 'p595dodmp01'
port = 1521
sid = 'DBUPA269'
username_cargois <- 'CARGO'
password_cargois <- '********'


#' RODBC MS SQL server connection string 
#' for BIO
driver_bio <- 'SQL Server'
server_bio <- 'fr0-bio-p01'
port_bio <- 10335
username_bio <- ''
password_bio <- ''
trusted_connection_bio <- TRUE # if TRUE connect with windows login and pw


#' RMySQL MySQL connection string 
#' for FlightRadar 24
user_fr24 <- "user_ext"
password_fr24 <- "************"
dbname_fr24 <- 'FR24'
host_fr24 <- "fr0-dmds-p01"
```

* Step 3: Now you can open RStudio.
    
    + Before running **CDM**, if you have more than one version of R installed on your computer, make sure that the R version is `[64-bit] ~/MRO_3.2.5` (the name could be varied)

    + Click on the **run** button on the top right of the text editor aera to execute the application. The application will automatically check if all the required R packages are installed and it will install those which are not installed from [**CRAN** (Comprehensive R Archive Network)](https://cran.r-project.org/). **CRAN** is a network of ftp and web servers around the world that store identical, up-to-date, versions of code and documentation for R. However, due to the internet connection configuration inside Airbus, if any of the required packages fails to download, you will have to download and install it manuelly (See Appendix for detail).
    
Now you are ready to use **CDM** :)
    
## Deployment on a Shiny Server Pro

**Shiny Server Pro** is a server program that makes Shiny application available over the web.

At this time, Shiny Server can be run on Linux servers with explicit support for Ubuntu 12.04 or greater (64 bit) and CentOS/RHEL 5 (64 bit) or greater. Multiple Shiny applications on multiple web pages could be hosted with the same Shiny Server.

It can be downloaded from [https://www.rstudio.com/products/shiny/shiny-server/](https://www.rstudio.com/products/shiny/shiny-server/).

For the detail instruction of the configuration and installation of Shiny Server Pro, see [**Shiny Server Professional v1.4.2 Administrator's Guide** on http://docs.rstudio.com/shiny-server/](http://docs.rstudio.com/shiny-server/).

# Structure and Features

A Shiny dashboard application could contains three sources scripts:

* a user-interface script: `ui.R`
* a server script: `server.R`
* a global environment script: `global.R`

There is another structure of Shiny application where all the three main scripts could be integrated into one single script `app.R`. But here we only talk about the "traditional" structure.

The UI script controls the layout and appearance of the app. The server script contains the instructions that your computer needs to build your app. And the global script defines objects in the global scope.

**Reactivie programming** is the fundamental of a Shiny Dashboard application. The main idea is to make it easy to wire up *input values* from a web page, trigger the R code to be (re)executed, and then have the results of your R code be written as *output values* back to the web page.

The following figure shows the three elements in Shiny reactive programming. **Reactive source** typically is the user's input through a web browser. It could trigger the execution of an R code. The output of the code is represented by the **reactive endpoint**. **Reactive conductor** could be placed between the sources and endpoints. Generally they are used to encapsulate the computationally expensive operations in order to augment the code performance. 

\begin{figure}[!h]
  \centering
  \includegraphics[width=300px]{img/roles.png}
  \caption{Essential objects in reactive programming}
\end{figure}

After launching **CDM**, you will see the following welcome page. **CDM** has three parts: a header, a sidebar and a body. The header show the application name and some notification[^1], for example the database connection status, the app version and the developing progress. The sidebar could help you to navigate between different tabs The functionalities of these widgets will be presented in the following sections. Finally the body is the main area where you will be able to interact with **CMD** and see the output.

<!--- #TODO: ADD THE IMAGE OF HOMEPAGE CDM -->
\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/welcomePage.png}
  \caption{\textbf{CMD} home page}
\end{figure}

Five different tabs are displayed on the sidebar. Each tab contains also several sub-tabs. 

## Cargo IS Database

[**Cargo IS**](http://www.iata.org/services/statistics/intelligence/cargois/Pages/index.aspx) database is the first major component of **CDM**. It provides airport level Air Waybill data, including airfreight charges, weight, numbers of shipments and it is the only resource of cargo yield information for Airbus. 

The database is stored on the server **p595dodmp01**, under the user folder **A269_CARGOIS**. The main data table is `CARGOIS_MONTHLYDATA`, which contains 33 columns. But only few of them contain usable information for analysis. `r paste(strsplit("WEIGHT_BREAK
ORIGIN_AIRPORT_CODE
DESTINATION_AIRPORT_CODE
SALES_YEAR
DESTINATION_CITY_CODE
ORIGIN_CITY_CODE
SALES_MONTH
ORIGIN_COUNTRY_CODE
WEIGHT_CHARGES_CURR_YEAR_USD
OTHER_CHARGES_CURR_YEAR_USD
WEIGHT_CURRENT_YEAR
AWB_COUNT_CURRENT_YEAR
GREATCIRCLEDISTANCE_KM", "\n")[[1]], sep = ", ")`

**Important**: The database that we purchased does not contain any airline information. But a column called `AIRLINE_PREFIX` presents in the data table. It may be possible to negotiate with IATA to get the airline information in the future.

### Data loader 

#### Instruction

The first step is about how to load Cargo IS data. In the first drop-down menu, we could select the level of data granularity to be queried from Cargo IS (*e.g.*, airport to airport, country to country, region to region, etc). Then the year and the **O&D** (**O**rigin and **D**estination) of airfreight should be precised. You can check the box *"Plot evolution since 2010"* to load data of all the available year (2010-2016). When the box is checked, the year input will be ignored.

After selecting the right parameters, click on **Load Data** button. Some summarize of the queried dataset will be shown on the top of this tab. A preview of the 50 first rows will appear on the right. You could do a quick check of the data. The data table could be downloaded by simply clicking on the **Download Data** button.

Now the data table is loaded and ready to be used!

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/cargois_load.png}
  \caption{An example query of the 2015 airfreight from \textit{China} to \textit{the USA}. }
\end{figure}


#### Explaination

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/flowchart_cargois_dataloader.png}
  \caption{Flowchart of data loading process}
\end{figure}


The data loading procedure will call the `CargoIS.SQL.query` function. The function will take the user parameters as inputs, generate an appropriate `Oracle SQL` code and send the query to the data server. The returned dataset is thus stocked in the global scope and it is ready to be used by other functions.

```{r eval=FALSE, echo=TRUE}
# EXAMPLE
# Query airfreight data of 2015 with origin country = China, destination = USA 
dat <- CargoIS.SQL.query(CargoDB, level = 'C2C',
                         ORG = 'CN', 
                         DST = 'US',
                         year = 2015)
```

The six value boxes on the top of the page are created by the function `valueBox(value, subtitle, icon, color, width, href)` based on the output dataset. They represent: 

* **Airports**: Numbers of unique airports appeared in the dataset.
* **Air routes**: Numbers of unique airport pairs (Origin + Destination) in the dataset.
* **Origin country**: Numbers of unique origin country(ies).
* **Destination country**: Numbers of unique destination country(ies).
* **AVG monthly weight**: Arithmetic mean of weight.
$${Average\ monthly\ weight} = \frac{\sum_{i=1}^n \sum_{j=1}^m {weight}_{ij}}{n}$$, where *i* is the number of months, *j* is the weight break.
* **AVG gross/net yield**: 
$${Average\ gross\ yield} = \frac{\sum_{i=1}^n \sum_{j=1}^m {charges}_{ij} + {surcharges}_{ij}}{\sum_{i=1}^n \sum_{j=1}^m {weight}_{ij}}$$

$${Average\ net\ yield} = \frac{\sum_{i=1}^n \sum_{j=1}^m {charges}_{ij}}{\sum_{i=1}^n \sum_{j=1}^m {weight}_{ij}}$$, *charges* are fees directly related to the weight of the shipment and *surcharges* contain all the other fees (fuel surcharges, security surcharges, taxes, etc.)

### Top airports/air routes
When the data loading procedure is complete, you can go to the following tabs to see some visualization output. After clicking on the "Yield Analysis" tab, **CDM** will automatically proceed and visualize the loaded dataset.

#### Instruction
\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/cargois_top_airport.png}
  \caption{Yield Analysis tab, top 20 airports of CN-US}
\end{figure}

The first part of tab contains visualization of the **top *n* airports and air routes**. Figure 6 shows in the map the top 20 origin and destination airports. The surface of the circle represents the weight of shipment going through this airport. The darkness of the color represents the yield of the airport. The charts are interactive, you can zoom in/out with the mouse scroll wheel. You can also click on the legend to display/hide the origin/destination airports.

The value of *n* could be modified by dragging the slider bar. You could also modify the size of the circle if sometimes the default size is too big/small.

The **Top air routes (O&D)** tab of the visualization chart shows the weight and yield of the most important air routes. Origin and destination airports are linked by blue curves with different thickness and darkness. The **thicker** the curve, the **more** the total weight and the **darker** the blue, the **higher** the yield.

The last two tabs (Airports data table and Air routes data table)show the two data tables that **CDM** uses to create the map. It could be sorted by variables and it could be directly copy-pasted into an Excel sheet.

#### Explaination
An R package `Plot_ly` was used to create the visualization map. From `/Scripts/Plot.airport.html.R`, an user defined function `Plot.airport.html()` is called. 

```{r eval=FALSE, echo = TRUE}
#' [Plot.airport.html] could be used to visualize the top n airports/air routes
#' When the parameter table = TRUE, it will output the datatable that it will 
#' use for the data visualization.
#'
#' @param dataset: data frame with five columns
#' c('ORIGIN_AIRPORT_CODE', 'DESTINATION_AIRPORT_CODE', 'WEIGHT_CURRENT_YEAR', 
#' 'WEIGHT_CHARGES_CURR_YEAR_USD', 'OTHER_CHARGES_CURR_YEAR_USD')
#'
#' @param projection: Mercator or orthographic
#'
#' @param top: numbers of airport/air routes to be displayed
#'
#' @param plot.airport: if TRUE, plot airport, if FALSE, plot air routes
#'
#' @param pt.size: int, point size
#'
#' @param table: if TRUE, output datatable, otherwise, output map

 Plot.airport.html(dataset, projection = 'Mercator', top = 20, plot.airport = TRUE, 
                   pt.size = 800000, table = FALSE)
```

`Plot.airport.html()` will call `plotly::plot_ly()`. `plotly::plot_ly()` provides a simple way to add scatters/lines/curves to a map. It will only need the coordinates of the O&D airports, which we could easily get from BIO database by doing

```{r eval = FALSE, echo=TRUE}
source('/Scripts/get.airport.loc.R')
get.airport.loc()
```

Figure 7 shows how the function `plot.airport.html()` works.


\begin{figure}
  \centering
  \includegraphics[width=470px]{img/flowchart_cargois_top.png}
  \caption{Flowchart of top airports/air routes tab}
\end{figure}


### Treemap

#### Instruction
\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/cargois_yield2.png}
  \caption{Treemap of airports for CN and US}
\end{figure}

The tab **Treemap** visualizes the relationship between different **nodes** (airports, countries and regions). Each node is displayed as a rectangle, sized by the total airfreight weight of this node and colored by the average gross yield of the node.

You can click on the rectangle to see its child nodes[^2] (if exist), and right-click to see its parent node. A scale is shown on the top right to indicate the yield level. The tab **Table** will render the used data table for the visualization. The table contains four columns, *Name*, *Parent*, *Weight*, *GrossYield*. 

Currently there is no optimal solution to generate a static downloadable image. So you may take a screen shot if you want to add the chart to your slides. 

#### Explaination

\begin{figure}
  \centering
  \includegraphics[width=270px]{img/flowchart_cargois_tree.png}
  \caption{Flowchart of Treemap tab}
\end{figure}

To create an interactive treemap, I created an user-defined function `treemap_cargois_gvis()`, which will call `googleVis::gvisTreeMap()`. The package `googleVis` is the R interface to **Google Charts API**. It generates an HTML code which could be integrated into R Shiny application. It could be further customized by using Javascripts.

```{r eval=FALSE, echo=TRUE}
# Example:
treemap_cargois_gvis(data, ORG = FALSE, PLOT = TRUE)

#' data is a data.frame object generated by Cargois.SQL.query()
#' If ORG = TRUE, then create treemap for the origin airports, 
#' else for the the destination airports
#' If PLOT = FALSE, then the output will be a data.frame object 
#' (instead of a plot)
```

The function `treemap_cargois_gvis()` will convert the queried Cargo IS data table into a four-column dataset (*Name*, *Parent*, *Weight*, *GrossYield*), which could be used by `googleVis::gvisTreeMap()`.

```{r eval=FALSE, echo=TRUE}
# Example of gvisTreemap
gvisTreeMap(data = datatable, idvar = 'Name', parentvar = 'Parent', sizevar = 'Weight',
                colorvar = 'GrossYield',
                options=list(fontSize=16, 
                             minColor='#F5B041',
                             midColor='#F0F3F4',
                             maxColor='#5499C7',
                             headerHeight=20,
                             fontColor='black',
                             showScale=TRUE)
                            # options, see 
                            # https://developers.google.com/chart/interactive/docs/
            )
```




### Yield Evolution
<!-- what is yield? how to calculate? how can we use it? -->
Yield is the most important information provided by Cargo IS database. 

#### Instruction

<!-- Add details about the table tab: colnames, structure--->

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/cargois_yield3.png}
  \caption{Airfreight weight and yield evolution for CN and US}
\end{figure}

The next tab **Yield evolution** generates an airfreight evolution plot. **CDM** calculates and render a line chart showing the evolution of gross yield, net yield and airfreight weight during the selected period of time. The minimum, maximum and average value of the output are shown in the plot's subtitle. 

The x-axis represents the available months during the selected period. If the box "Plot evolution since 2010" in the data loaded page is checked, all the available data will be visualized (but the computing will also take a longer time).

You could click on the curve to see detailed information of the chosen data point.

A data table appears on the bottom of the page. It contains all the data of the line chart. You could click on the download button to save it to the local.

#### Explaination

I would like to integrate the three curves (net yield, gross yield and weight) into one single chart. Thus two different y-axis are needed. The well known package `ggplot2` does not support two different y-axis in one chart so I will still use `googleVis` to generate the line chart.

```{r eval=FALSE, echo=TRUE}
# Example of givsLineChart
# with gvisLineChart, we could easily create a line chart with 2 y-axis

gvisLineChart(data, xvar = "xaxis", yvar = c('yaxis_1', 'yaxis_2', 'yaxis_3'), 
              options = list(series="[
                               {targetAxisIndex: 0}, # set the target y-axis
                               {targetAxisIndex: 0},
                               {targetAxisIndex: 1}
                               ]"
                             )
              )
```

### Air Waybill Analysis

An **air waybill** is a receipt issued by an international airline for goods and an evidence of the contract of carriage. It is the most important document issued by the carrier (directly or through an authorized agent). Cargo IS contains the records the weight data and it regroups the air waybills into six categories, which are called **weight breaks**, regarding to its weight.

They are:

* 0 to 50 kg
* 50 to 100 kg 
* 100 to 300 kg
* 300 to 500 kg 
* 500 to 1000 kg
* larger than 1000 kg

The proportion of the AWB of different categories in a market could be an indicator of the economic situation. For example, an increasing number of heavy shipments often means the cargo consolidation becomes more efficient, and the economic situation is going better.

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/cargois_AWB.png}
  \caption{Air waybill analysis}
\end{figure}

#### Instruction

The first row of this tab contains seven figures:

- *Shipment frequency evolution* is a line chart which shows how the numbers of shipments change during the selected period. By default, there will be six curves representing respectively the different weight break.
- *Shipment weight distribution* is a bar chart which shows the distribution of the AWB of different weight break in the selected period.
- *Weight vs. distance* is a stacked bar chart showing the sum of shipment weight by different intervals of distance. The colors represent the different weight breaks.
- *Frequency vs. distance*: like the previous figure, it shows the numbers of shipments by different intervals of distance.
- *Revenu vs. distance* shows the revenues (charges) of airfreight by different intervals of distance.
- *Yield vs. distance* is a line chart showing the gross/net yield of by weight breaks and by distance.
- *Average weight vs. distance* takes into account all the weight breaks and compute the weighted arithmetic mean of weight by distance.

For the charts 3, 4 ,5 and 6, if there is only one interval of distance, a pie chart will be created instead of a bar chart. All the charts can be downloaded by clicking "download PNG" button.

On the left of the charts, some parameters can be changed to modify the charts. You can display/hide one or multiple weight break(s) by checking/unchecking the boxes. The second part "gross yield/net yield" corresponds to the yield type in the chart *Yield vs. distance*. The last two text input area control the width and height of the downloaded image. 

On the bottom of the page, the data table used for creating the charts is displayed. It could also be downloaded by clicking the download button.

#### Explaination
<!-- TRY TO USE data.table -->
Before creating the charts, data manipulation should be done in order to have the right data to plot. `data.table` is a very powerful package for big data computing.

```{r eval=FALSE, echo=TRUE}
# Example of data.table

system.time(
  output <- dt[,.(weight = sum(WEIGHT_CURRENT_YEAR), 
                freq = sum(AWB_COUNT_CURRENT_YEAR),
                wchg = sum(WEIGHT_CHARGES_CURR_YEAR_USD),
                surchg = sum(OTHER_CHARGES_CURR_YEAR_USD),
                gy = (sum(WEIGHT_CHARGES_CURR_YEAR_USD)+
                         sum(OTHER_CHARGES_CURR_YEAR_USD))/sum(WEIGHT_CURRENT_YEAR),
                ny = (sum(WEIGHT_CHARGES_CURR_YEAR_USD))/sum(WEIGHT_CURRENT_YEAR)
                ), by = .(dist = lebal, wb = WEIGHT_BREAK)
              ]
)
# dt is a 1 750 000*15 data.table,
# user  system elapsed 
# 0.14    0.00    0.14 
```

To create these charts, the package `ggplot2` is extensively used. 

### Yield Calculator

The last sub tab of Cargo IS is a marketing tool called yield calculator, which offers an automatic computing for air route cargo yield. It will read air routes from a `csv` file (uploaded by user), query *Cargo IS* database and display a data table with weight and yields of every air route in the uploaded list, as well as a air route map visualizing all the air routes by their cargo weight and cargo yield.

#### Instruction

The idea of yield calculator is to get rid of manual cargo yield computing. To use yield calculator, you will need to create a `csv` file containing two columns: "From" and "To", which correspond to the origin and destination airport. Once the `csv` is ready, you could upload it to **CDM** by clicking **choose file** button. Then, the year parameter should be selected. The others parameters could be modified if according to the format of your `csv` file. When everything is done, click on *Start*.

A data table will be displayed after the computing. The gross yield, net yield, weight, gross charges and net charges will be calculated for each air route. On the bottom, an air routes map will show the input air routes by the cargo weight and cargo yield. The darker the curve, the higher the yield. The thicker the curve, the higher the cargo weight. Click on "Download" to download the data table. It will be a `csv` file as well. 

There may be rows only containing value **zero** in the output table. It is because of the lack of data in Cargo IS database. We do not have any information about the given air route.

On the left of the map, there are some display parameters. You can select the appropriate map projection, the comparing criteria and some graphical parameters to customize the map.

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/cargois_yld_cal.png}
  \caption{Yield calculator interface}
\end{figure}

#### Explaination

Figure 13 show the data manipulation procedure. Two input are used. The first one is the uploaded `csv` file and the second one is the Cargo IS data of the selected year (queried by `CargoIS.SQL.query()`). The function `grs_net_yield2()` calls the package `data.table` and computes cargo yield for every air route of this data table. The yield table will be left joined to the uploaded air route list. After merging, the data table will be displayed on the top right of the page and the function `Plot.air.route.html()` will be call to further generate a map.

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/flowchart_cargois_yld_calculator.png}
  \caption{Flowchart of yield calculator}
\end{figure}



<!-- _________Seabury database__________ -->
## Seabury Database

The second part of this document consists analysis and visualizations of **Seabury Trade** database. Seabury Trade contains annual country level cargo weight and value information. It has not only the airfreight weight and value, but also for the other surface transportation. It provide an in-depth level of commodity type which could allow us to get some knowledge about the cargo type of the market.

Beside Seabury trade, there two other databases which could be useful for market knowledge. They are Seabury Express and Seabury. They could be very useful for the further development of the application.

Seabury databases are stored in the same data server as Cargo IS. 

### Data loader

#### Instruction

As for Cargo IS query, the first step here also consists of data loading. You must select firstly the data granularity to be queried. Then, the year parameter should be set as well. Seabury Trade database contains annual data from 2000. Then the drop menus of *Origin* and *Destination* will change automatically according to your selection of data granularity. When all the input parameters are set, click on the **Run** button to start to query the database.

#### Explaination

The start button triggers the user-defined function `Seabury.SQL.OD.query()`. It works just like `CargoIS.SQL.query()`: it will generate a SQL query that depends on the user input. Then it send the generated query to our SQL server and fetch the returned data.

```{r eval=FALSE, echo=TRUE}
# Example
#' ODBC: a Oracle SQL connector,
#' level: granularity of queried data
#' ORG: Origin
#' DST: destination
#' Year: interger of NA, if NA, query all the data, otherwise query the selected year
#' country.name: if TRUE, return the full country name
Seabury.SQL.OD.query(ODBC, level, ORG, DST, year = NA, country.name = FALSE)
```


### Commodity treemap

Seabury Trade database contains a detailed commodity categorization system. It has eight main categories and more than 2000 sub-categories. 

#### Instruction

Seabury Trade has more than 70 000 000 rows so the data loading process may take longer time than Cargo IS. When data is loaded, **CDM** will generate a treemap to present the commodity types, their weight (in kg) and their value (in USD). The size of the square corresponds to the cargo weight for this type of goods. Its color represent the value. The data table could be view in the *Table* tab, and you could download it by clicking on the button *Download*. The structure of the data table is the same as the airport treemap in Cargo IS.

You can click on the square to look further into the sub-categories of the selected commodity type. There are four different levels of categories, G1, G2, G3 and G4. The bigger the number, the higher the complexity. G1 level contains eight different categories but there are around 2000 in the G4 level.

You could change to look at the ocean freight information by simply selecting the freight type from the drop-down menu. The data table is also downloadable by clicking **Download** button.

#### Explaination

To draw the treemap, a user-defined function `treemap_dt_sea_gvis()` is firstly called to generate a data table that fits the requests of `googleVis::gvisTreeMap()`. Then the treemap is generated with a user-defined function `treemap_sea_gvis()`, which will call `googleVis::gvisTreeMap()`. 

```{r eval=FALSE, echo=TRUE}
# Function to generate data table for treemap of SEABURY GXCODE
#' data: an output datatable of Seabury.SQL.OD.query()
#' if AIR = TRUE then output airfreight value
#' otherwise, output surface freight value
treemap_dt_sea_gvis(data, AIR = TRUE)

#' Function to draw the treemap of SEABURY GXCODE
#' data: Output of treemap_dt_sea_gvis()
#' ORG, DST, YEAR: parameter of the title of the treemap
treemap_sea_gvis(data, ORG, DST, YEAR)

```


### Evolution plot

We may be able to predict the future by learning from the history. So it will be useful to know how the cargo weight/value of some specific commodities evolve during the last years. 

#### Instruction
The second major functionality of Seabury Trade tab is the cargo weight evolution plot. By selecting the name of commodity type, you can thus create a line chart that represents the evolution of airfreight weight since 2000. If the box "Plot all level" is checked, then all the data base will be loaded and visualized (This could take a very long time).

There are four sub-tabs (G1LEVEL, G2LEVEL, G3LEVEL and G4LEVEL) representing the four different categories. The evolution of the sub-categories (if exist) of the selected type will be plotted following sub-tab. You can change the y-axis from cargo weight to cargo value.

<!-- TODO: download datatable -->
The data table will be displayed in the last sub-tab.

**Attention**: If you selected, for example, a G3 level category, then please go the the third sub-tab (G3LEVEL) to get the corresponded line chart. The charts in the superior levels will be the same as the third tab, but the commodity name will be wrong. To know the level of category that you selected, you can count the number of "-" before the name of category.

#### Explaination

The evolution plot of will use all the Seabury data starting from 2000. The user-defined function `Seabury.SQL.evo.query()` will query the data base and stock the returned data table into the reactive variable `DATA.SEA.GX()`. Then the function `sea.evo()` will be called to sum the weight and value by year and by commodity type (According to the input, it will sum the air freight or the ocean freight data). `Seabury.SQL.get.name()` will return the full name of the commodity types and the names will be added into the data table as a new column.  At the end, `Plot_ly()` will be used to create the evolution line chart. 



<!-- ____________FlightRadar 24___________ -->
## FlightRadar 24 Database

**FlighRadar 24** (FR24) is a recently purchased database at Airbus. It is a Swedish internet-based service that provides aircraft flight information. The database that Airbus purchased from FR24 includes flight tracks, origins and destinations, flight numbers, registration numbers, flight positions (coordinates), altitude, heading and speed during 2014 and 2015. The data of FR24 mainly comes from the third party ADS-B (Automatic dependent surveillance-broadcast) receivers all over the world. The receivers collect data from any aircraft in their local area that are equipped with an ADS-B transponder and upload to the internet in the real time. 

FR24 could be very valuable for Airbus freighter because it may fill the gap of the lack of express cargo airlines' data. In an other flight schedule database **OAG**, there is no data for express cargo airlines (like **UPS**, **FedEx** or **DHL**). However with FR24, we may be able to extract the real flight program <!--what is the right word?--> of these airlines, which we did not have any information before.

But, comparing with other databases, it has some particularities. 

* We have two stock location for this database. The first one is the **MySQL** server inside airbus (which is used by **CDM**). The second one is the cloud-based platform **Foundry** (could be queried by SparkR on Foundry). 

* The data size is way larger than the other databases. Because it records the real-time position of aircraft, so we have about 1-2 Gb of data per day. **CDM** mainly uses the air routes data (which means Origin-Destination information). So I could still manipulate the data on my own desktop. But in the future, if we will need to use the position data of FR24, more computing capability will be necessary. 
<!-- ask aur?lien -->

* The data quality of FR24 is a major challenge for analysis. For example here I list three major problems of the database:
    
    1. Missing values in the data table are very frequent.

    2. There may be several different values indexing one same thing (*e.g.* In the column "Aircraft Type", both B77F, B77L, 77L and 77F represent Boeing 777 freighter).

    3. The data could be merged incorrectly at the very beginning of ADS-B raw data manipulation (*e.g.* the aircraft type of an aircraft registration number is not correct). This could be a problem of FlightRadar24 raw data.

These problems should be solved through two approaches. On one hand, we must return our feedback to FR24 in order to improve the data quality in the raw data level. On the other hand, inside Airbus, we will need to find a efficient method to detect and correct abnormal values in the database (See the section *Further development* for more details.)

### Data loader

Due to the insufficient data quality, the data loading process of FR24 will be a bit more complex than the two previous databases. It will be done in two step.

First of all, **CDM** queries FR24 database according to user's input. Then, it will merge FR24 data with our BIO data by the registration number, in order to improve the data quality.

#### Instruction

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/fr24_dataloader.PNG}
  \caption{FR24 data loader}
\end{figure}


To load the database, you have to precise the data range (by clicking and navigating through the data range selection panel). Then there are several parameters can be set according to the user's need (none of the following parameters is obligatory).

* Airline: Select the airline(s) that you want to query

* Origin: Filter by the origin airport.

* Destination: Filter by the destination airport.

    + If Destination is missing, **CDM** will query all the flights that leave the origin airport
    + If Origin is missing, it will query all the flights that fly to the destination airport
    + If Origin is the same as the Destination, it will query all the flights of the selected airport
    + If both Origin and Destination are missing, it will not filter the data by O&D
    
* Registration number: Filter by the aircraft registration number(s)

* Aircraft type: Filter by the aircraft type(s)

By modifying the parameters, **CDM** generates automatically a SQL query that corresponds to your request. And the query text is showed in the text area. If you are familiar with MySQL, you can directly modify it in the text box to create a more customized query. To solve the problem 1, the query will ignore all the data with a missing origin or destination.

Then click on the button **Query** to query FR24 database. The summary of FR24 data will be showed on the top right of the current tab. Then on the bottom of the page, a new box called *Data Cleaner* will appear. It will allow you to further remove the outliers in the returned data table in order to solve the problem 3.

After selecting the appropriated parameters in data cleaner box, click on the blue button **Enrich with BIO** to query BIO and merge it with the FR24 data table. The idea is to used the cleaned BIO data to replace the original data in order to solve the problem 2. A bar chart will appear on the top right showing the distribution of a selected variable. Here again, you could check the data quality and remove the outliers by looking at its frequency.

The merged data can be downloaded by clicking on the download button.

#### Explaination

\begin{figure}[!h]
  \centering
  \includegraphics[width=470px]{img/flowchart_fr24_dataloading.png}
  \caption{The data loading process of FR24}
\end{figure}

FR24 is stocked on a MySQL server inside Airbus. So the first step is to generate a SQL query that fits user's request. By using logical operators and string manipulation, the output query string is stored in `FR24_query()`. The text area shows the content of `FR24_query()` and could be modified by keyboard. 
Then, when the button **Query** is clicked, `input$go2_fr24` will trigger the SQL query. The query result will be stocked in `FR24_datatable()`. The info-boxes will be created based on some descriptive statistics and the preview of data table will be returned as well.

Because of the data quality, I would like to create another filter process to detect the outliers in the data in order to further refine the data quality. The idea is to return the abnormal value in the **Data cleaner** box and let the user decide whether to keep it or not.

  * Registration number: The aircraft registrations are strings containing five or six characters. To detect the abnormal value, I used the package `stringdist` to compute the **Jaro-Winkler** distance between each of these numbers. Then I cluster these registration numbers based on the distance matrix. I list the least presented clusters to the user so that the user could select and remove the incorrect values.
  
  * The other three variables contains normally less values than the registration number, so they could by entirely listed and selected by user.
  
When the button **Enrich with BIO** is clicked, it will trigger the query of BIO database (**CDM** will match the BIO data by the registration number in FR24 database) and a data table containing detailed information of the aircraft will be returned and stored in `FR24_BIO_AC()`. You will see the preview of data table `output$BIO_fr24` and a bar chart `output$fr24_freq_check_dt_quality`.

### Airline network

#### Instruction

\begin{figure}
  \centering
  \includegraphics[width=470px]{img/fr24_airline_network.PNG}
  \includegraphics[width=470px]{img/fr24_airline_airports.PNG}
  \includegraphics[width=470px]{img/fr24_airline_heatmap.PNG}
  \caption{Network visualization for FedEx Boeing 777 Freighter}
\end{figure}


<!-- add coordinates of airport  -->
A map showing the location of every airport in the queried FR24 data table will be displayed after the data loading process. You could click on the markers to see the airport IATA code and airport name. In the tab **Network Analysis**, the network of the data table will be extracted and visualized.

Every circle on the map represents an airport. The size represents its importance in the network. All the circles are colored by their corresponding region. You can filter the airports by their regions by clicking the drop-down menu on the top left.

The arrow shows the direction of the airfreight flow. 

You can click on an airport to filter all its neighbor airports (airports that are directly linked to this airport). You can also drag the circle to change its position. 

In the third tab analysis, you will see a heatmap showing the distance (minimum numbers of flight) between the airports and a tool to find the shortest path in terms of numbers of flight. You can select the origin and the destination from the two drop-down menus. For the heatmap, the darker the blue, the shorter the path. If the color is white (no matter what the value of $z$ is), it means that there is no flight in between.

#### Explaination

Once the reactive value `FR24_BIO_AC()` is created, **CDM** will create `FR24_NW_NODE()`, `FR24_NW_EDGE()` and `FR24_NW_igraph()`. They are three datasets that will be used to generate network visualization.

The airport map is created by using an R package `Leaflet`. It is an API of the open-source JavaScript library in R. It uses *OpenStreetMap* data to create interactive map. The R package contains only a part of its features, further development could be done by written directly on JavaScript.

```{r eval=FALSE, echo=TRUE}
# EXAMPLE: output$fr24_airline_network_map
# airport is a dataframe containing airports name, longitude and latitude
leaflet(airport) %>% 
      addTiles(urlTemplate = "YOUR MAPBOX TEMPLATE",
               attribution = 'YOUR ATTRIBUTION') %>%
      addMarkers(~long, ~lat, popup = ~htmlEscape(paste(IATA,name, sep = ": ")))

```

The network visualization is created by using `visNetwork` package. It takes `FR24_NW_NODE()`, `FR24_NW_EDGE()` as the *nodes* and *edges* parameters.

`FR24_NW_igraph()` is a `igraph` object created from the adjacency matrix (which was created by `igraph::get.adjacency()`). It is a directed, non-weighted adjacency matrix. I used to take the air routes frequency as the weight, but it will lead to some results that do not have any sense. For example in the shortest path computing, if we take into account the frequency of air routes, the shortest path will contain the more "important" air routes instead of the shortest path. For future development, we may add the read great circle distance of the air routes and find a model that determines the weight of air route.

`FR24_NW_igraph()` is thus used for the computing of distance matrix and the heatmap visualization.

### Airport traffic*

This tab provides airport traffic information. You will see the take-off rate of the selected airport, the numbers of grounding aircraft, the congestion status, etc.

### Aircraft utilization*

In this tab, you can check for each selected aircraft, its utilization (flying time), grounding time and missing time (period that we do not have any information).

You will see the most frequent air routes of the aircraft as well.

## Other features

### Connection status check

The first link icon on the top right shows the connection status of **CDM** to the databases. If all the databases are successfully connected, the color around the number will be blue. Otherwise the background color will turn red.

You can click on the icon to see the detailed connection information.

\begin{figure}[!h]
  \centering
  \includegraphics[width=350px]{img/connection_status_OK.png}
  \caption{Connection succeed/failed}
\end{figure}

#### Explaination 

Each time when a new session of **CDM** starts, it will try to make a connection to these databases and check the class of the connector by using `try()`. It will return "try error" in the case that the connection to databases could not be established.

```{r eval=FALSE, echo=TRUE}

CargoDB <- try(dbConnect(drv, username = username_cargois, 
                         password = password_cargois, 
                         dbname = connect_string_cargois))

```

If the class of all the connectors are not `'try-error'`, the value `OK` will be given to the variables `statu_cargois`, `statu_bio` and `statu_fr24`, which will determine the color and the text output of the header's notification.

**IMPORTANT**: Functions related to a database will be loaded only if the database could be reached.

### Server-side selectize input

There are several different methods to have a reactive select input. For example `uiOutput() + renderUI({selectInput()})`. But in some situation, the input contains too many elements so that the performance of `renderUI()` may be insufficient. In this situation, `selectizeInput() + updateSelectizeInput()` will be very useful. 

```{r eval=FALSE, echo=TRUE}
# Example
# in ui.R
selectizeInput('foo', choices = NULL, ...)

# in server.R
shinyServer(function(input, output, session) {
  updateSelectizeInput(session, 'foo', choices = data, server = TRUE)
})
```

The server-side `selectizeInput` uses R to process searching, and R will return the filtered data to `selectize`. It is widely use in **CDM** and it greatly boosts the interactive performance.

### User session log (still under development)

The idea of this feature is to create a interface where the experienced R user could get the system log information and interactive with R by coding. But now I still did not find a way to capture the R console's output and return it into **CDM**. Now you can only call a "so-called" console of **CDM** by pressing the `~` button of your keyboard. It will display your detailed connection status.

This feature is done by using a JS script.
```{r eval=FALSE, echo=TRUE}
# ui.R
fluidRow(
         htmlOutput("consol"),
         tags$script('
                     $(document).on("keypress", function (e) {
                     Shiny.onInputChange("key_track", e.which);
                     });
         ')
)

# server.R
output$consol <- renderUI({
    show = FALSE
    if(is.null(input$key_track)){
    } else if (input$key_track == 126) {
      show <- TRUE
    }
    if(show){
      HTML('<!-- HTML CODE HERE -->')
    } else {
      p('')
    }
  })
```


# Future Development

Several functionalities and features of **CDM** is still under development. Some existing features could be improved and new functionalities could be added. 

## Improvement of existing features

### Speed up data processing

  * Some functions still use `data.frame` objects to manipulate data. In order to have a faster processing speed, the package `data.table` should be used extensively. 
  * Avoid using `cbind` to expanding existing data structures. Try always to initialize it and then fill them in.
  * Store the results and access them rather than repeatedly recalculating.
  * Instead of using loops, try to use `apply(), sapply(), lapply()`.
  * Try to use multiple-thread computing (with MRO or packages like `parallel` )

### Downloadable images

All the `ggplot2` chart could be downloaded. However, for the charts created with `googleVis`, we will need to find a solution to generate a static image that could be downloaded. For those which are generated by `plot_ly`, figure out the problem why sometime the button *download* does not work.

### Database connections

Optimize the control of existing connection, automatically close those which are not used any more to gain resources. 

### Data cleaner of FR24

Create a more accurate algorithm to detect the outliers of the data. Then, instead of using `selectizeInput()`, try to find a more pretty way to interact and filter the data.

Optimize the data loading process of FR24 to make it more intuitive. Try to avoid clicking twice on the button to get the final cleaned data table.

### Personalized error message

In some situation, **CDM** will stop running and crash if the data structure could not be created properly (for example, if the query result is empty). In these cases, render a personalized error message in order to avoid the crash of application.

### Color of the treemap and circle size of top airport map

Find a algorithm to allocate a more appropriate value that determines the color of squares in the treemaps and the size of circle in airport map.

Then, try to make the color of treemap horizontally comparable. This means that you will be able to compare the color in different treemaps. Now you can only compare the color within on treemap.

### Modulize the application code

Inspired by the article [Modularizing Shiny app code](http://shiny.rstudio.com/articles/modules.html), When **CDM** grows larger and more complicated, the complexity of code grows as well.

**Modules** should be used in order to make the code maintenance easier.

## New features to be added in the future

### A general chart creating tool

The idea is to make the data visualization power of R be usable for everyone. To do so, I would like to create a visualization tool that could generate a customizable chart from a user uploaded `csv` or `xlsx` file. The file contents could be varied.

### Standardise the definitions of variable

In **CDM**, the definitions of variable may vary according to databases. For example the definition of *region* in **Cargo IS** and **Seabury**. If we could have a standard and unique definition within **CDM**, then it will be possible to merge these databases and increase the dimension of data.

### Automated reports generator

Inspired by project *LiMA*, a report generator could be used for automatic generation of a `pdf`, `doc` or `html` file, which contains all the analysis results created in **CDM** (or even from an uploaded `xlxs` file). The R package `knitr` could be a good choice to do this task.


# Conclusion

**R Shiny Dashboard** provides a solution of a light-weight and customizable data analysis/visualization tool. It turned out to be a good choice to fit the requests of Airbus Freighter Marketing team. **CDM** is thus a first step in Airbus freighter department as the response to the company level movement of digitalization.

In this Digital Age, the revolutionary technologies opened us the door of sharing and collaborating. It dramatically changes the meaning of work, not only for individual people, but also for giant companies like Airbus. Digitalization **is not** only about having all the data. It is also about the way we do with our data, or with our business. 

Interaction is the key word of this age. Faster and easier exchanges of information, better adaptability, smarter business intelligence, and the most important, higher end-user productivity, all these could produce big benefits for our business. Airbus is just at the beginning of the data digitalization, to keep our competitive, challenges still remain.

The following are the domains that matter in my personal point of view:

  * **Cloud**: It is definitely the most important part of digitalization. It provides shared computer processing resources and data services, which could be easily and optimally allocated to user according to the demand.
  
  * **Collaboration**: We will need a platform to share, to work together in time. It should be possible for every employee to share their own project on the platform and all the others could become a contributor of it. 
  
  * **Big data**: Not only the quantity of data, but also the dimension of data is increasing exponentially. The data may seem very sparse and irrelevant to our business. New approach should be adopted to extract the maximum value from the data.
  
I am very glad to see that some initial attempts are already realized in Airbus. Not only **CDM**, other Shiny Dashboard application are created as well. We also have a new built platform **Foundry**, where we could use SparkR to work on the collective data, share our codes and contribute to other colleagues' project.

Always stay open-mind with new technologies, keep our infrastructure up to data, Airbus will be able to reach a higher goal in the Digital Age.

\newpage

# Appendix: Troubleshooting

## Install Oracle Database instance client 

**Oracle Database Instant Client (11.2.0.3) EN_W764** could be found in **PC Service**, or it could be [downloaded from http://www.oracle.com/technetwork/topics/winx64soft-089540.html](http://www.oracle.com/technetwork/topics/winx64soft-089540.html) (you may need to create an account to be able to download it). After downloading the client, extract it to a folder that you could find again.

If **CDM** could not be executed due to errors of Oracle instant client, you can check if the environment variables of Windows is set correctly by doing the following procedure.

* Open the properties window of the computer.
* Click on "**Advanced system settings**"
* Select the tab "**Advanced**" of the appearing dialog box.
* Click "**Environment Variables**" button on the bottom.
* Find the variable "**Path**", make sure that the path of your Oracle instance client is added. If not, add it.

\begin{figure}[!h]
  \centering
  \includegraphics[width=220px]{img/set_oracle_path.png}
  \caption{Check the "Path" system variable}
\end{figure}


If the problem still exists, check the [**ROracle** package installation instruction on http://cran.us.r-project.org/web/packages/ROracle/INSTALL](http://cran.us.r-project.org/web/packages/ROracle/INSTALL)

## Download and install an R package manually

Some of the R package could not be installed directly from **CRAN**, for example the package `ROracle`. In this situation, the manual installation will be needed.

Here I will show the installation process for `ROracle`.

* Firstly, download [`ROracle_1.2-1.zip` from *oracle.com* (http://www.oracle.com/technetwork/database/database-technologies/r/roracle/downloads/index.html)](http://www.oracle.com/technetwork/database/database-technologies/r/roracle/downloads/index.html)

* Secondly, place the .zip file into `~/CDM/Rpackages` and make sure that *Oracle Instant Client* is correctly installed.

* Then, instead of running 
```{r eval=FALSE, echo=TRUE}
install.packages('ROracle')
```

run 

```{r eval=FALSE, echo=TRUE}
install.packages('Rpackages/ROracle_1.2-1.zip', repos = NULL, type="source")
```

After the installation, the package could be called by 

```{r eval=FALSE, echo=TRUE}
library(ROracle)
```

# Bibliography
  
  * Patrick Burns, *The R Inferno*, [http://www.burns-stat.com/pages/Tutor/R_inferno.pdf](http://www.burns-stat.com/pages/Tutor/R_inferno.pdf)
  * Navarro, Gonzalo (2001), [*A guided tour to approximating string matching*](http://repositorio.uchile.cl/bitstream/handle/2250/126168/Navarro_Gonzalo_Guided_tour.pdf), ACM Computing Surveys. 33 (1): 3188. doi:10.1145/375360.375365
  * `Plot_ly` documents, [https://plot.ly/r/](https://plot.ly/r/)
  * `Google Chart` documents, [https://developers.google.com/chart/interactive/docs/](https://developers.google.com/chart/interactive/docs/)
  * `leaflet` documents, [http://leafletjs.com/reference.html](http://leafletjs.com/reference.html)
  
  
  
<!--- Footnotes -->
[^1]: Some features are still under development.
[^2]: For example, **country** is the child node of **region**, and it is the parent node of **airport**.